A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-21 fivebranes/index.tex
merge error

We will compute the pushforward using the prescription for pushing forward a $\cA^{\bu}_{F}$-module along a compatible submersion outlined in \cite{KormanThesis}. Recall that we have a THF structure on $M$, given by an involutive subsheaf $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$. The situation is summarized in the diagram below.

\[
  \begin{tikzcd}
    0 \ar[r] & F_{M}\cap T_{M/Z}^{\C}\ar[r]\ar[d] & F_{M}\ar[r]\ar[d]  & \pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
    0 \ar[r] & T_{M/Z}^{\C}\ar[r] & T_{M}^{\C}\ar[r] & T_{Z}^{\C}\ar[r] & 0.
  \end{tikzcd}
\]

@@

For brevity, let $F_{\mathring M/\R_{>0}\times Z} = F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}$ and $p^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus\pi^{*}T^{0,1}_{Z}$. Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{F_{\R_{>0}\times Z}}$-module.

The splitting affords an isomorphism of $C^{\infty}_{\mathring M}$-modules
\[
  \cA^{\bu}_{F_{\mathring M}}(\cL)\cong \cA^{\bu}_{F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{F_{{\mathring M/ \R_{>0}\times Z}}}\otimes \cL
\]

Accordingly, the differential splits

Note that since we have a complex of locally free $C^{\infty}_{\mathring M}$-modules, the (a priori derived) functor $(p|\mathring M)_{*}$ has several nice properties. We may commute it past the tensor product above. Moreover, we may apply the functor term-wise. The result is that the pushforward is given by

@@

\begin{prop}
  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
  \beqn
  \cA^{\bu}_{F_{\R_{>0}\times Z}}\left(H^\bu(\cA^\bu_{F_{\mathring M/ R_{>0}\times Z}}(\cL))\right)
  \eeqn

@@

@@

After complexification, the~six-dimensional and three-dimensional superconformal algebras are isomorphic to $\lie{osp}(8|4)$.
The even part of this algebra is $\lie{so}(8) \times \lie{sp}(4)$.
This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S^{6d}_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
It also contains the three-dimensional $\cN=8$ supersymmetry algebra whose odd part is eight copies of $S^{3d}$, the irreducible complex spin representation of $\lie{so}(3)$.

In the six-dimensional case, the holomorphic supercharge is a supertranslation 
\[
Q \in \Pi S^{6d}_+ \otimes \C^4 \subset \lie{osp}(8|4)
\]
which is characterized (up to equivalence) by the properties that $Q^2 = 0$ and that its image
\[
{\rm Im}\left(Q|_{\Pi S_+ \otimes \C^4} \right) \subset \R^6 \otimes_\R \C \cong \C^6
\]
is three-dimensional (spanned by the anti-holomorphic translations). 
The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.

Similarly, the minimal twisting supercharge in the three-dimensional $\cN=8$ supersymmetry algebra is an element $Q \in \Pi S^{3d} \otimes \C^8$ which is characterized (up to equivalence) by the property that $Q^2 = 0$ and that the image of $[Q,-]$ is two-dimensional. 
The cohomology of $\lie{osp}(8|4)$ with respect to this supercharge is also isomorphic to~$\lie{osp}(6|2)$.

In the untwisted situation, the symmetry of solutions to eleven-dimensional supergravity in the presence of fivebranes wrapping a six-dimensional affine subspace is exactly the superconformal algebra $\lie{osp}(8|4)$ (after complexification). 
Geometrically, this background is $AdS_7 \times S^4$.

In \cite{RSW} we have proposed a twisted analog of the $AdS$ background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes and membranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twists of the superconformal algebras we just discussed.

We will count the single-particle gravitational states in our eleven-dimensional model for the geometry resulting from backreacting twisted fivebranes and membranes.
As recalled above, such states have a symmetry by the twisted superconformal algebra $\lie{osp}(6|2)$.
We will enumerate states via choosing a Cartan in the bosonic subalgebra of the twisted superconformal algebra. 
We recall below how the bosonic piece of the algebra
\beqn
\label{eqn:gut}
\lie{sl}(4) \times \lie{sl}(2) \subset \lie{osp}(6|2) 
\eeqn
embeds as symmetries, or ghosts, of the eleven-dimensional theory in this twisted background.
The embedding is distinct for fivebranes and membranes.
We turn first to the fivebrane case.

\brian{enhance to E(3|6)}.

>>>>

We will compute the pushforward using the prescription for pushing forward a $\cA^{\bu}_{F}$-module along a compatible submersion outlined in \cite{KormanThesis}. Recall that we have a THF structure on $M$, given by an involutive subbundle $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$. The situation is summarized in the diagram below.
\[
  \begin{tikzcd}
    0 \ar[r] & F_{M}\cap T_{M/Z}^{\C}\ar[r]\ar[d] & F_{M}\ar[r]\ar[d]  & \pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
    0 \ar[r] & T_{M/Z}^{\C}\ar[r] & T_{M}^{\C}\ar[r] & T_{Z}^{\C}\ar[r] & 0.
  \end{tikzcd}
\]

@@

We wish to describe $\cA^{\bu}_{F}$-modules, for $F$ an involutive subbundle appearing in the top row of the above diagram. To make the burden less cumbersome, we will drop mention of the foliation and instead refer to the directions in which the leaves lie. Explicitly, let $\cA_{\mathring M/\R_{>0}\times Z} = \cA_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}$, $F_{\R_{>0}\times Z} = T_{\R_{>0}}\oplus T^{0,1}_{Z}$ and $\cA_{\R_{>0}\times Z} = \cA_{\pi^{*} F _{\R_{>0}\times Z}}$. Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.

The splitting affords an isomorphism of $C^{\infty}_{\mathring M}$-modules
\[
  \cA^{\bu}_{\mathring M}(L)\cong \cA^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}\otimes \cL
\]

Note that since we have a complex of locally free $C^{\infty}_{\mathring M}$-modules, the (a priori derived) functor $(p|\mathring M)_{*}$ has several nice properties. We may commute it past the tensor product above. Moreover, we may apply the functor term-wise. The result is that the pushforward is given by \surya{finish}

In \cite{KormanThesis}, the THF differential $\thfD$ on $\cA^{\bu}_{\mathring M}(L)$ is interpreted as defining a superconnection on the pushforward $\pi_{*}\cA^{\bu}_{\mathring M/R_{>0}\times Z}$ viewed as the sheaf of sections of a complex of pro-vector bundles on $\R_{+}\times Z$.

\surya{finish}

@@

\begin{prop}
  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
  \beqn
  \cA^{\bu}_{F_{\R_{>0}\times Z}}\left(H^\bu(\cA^\bu_{F_{\mathring M/ R_{>0}\times Z}}(\cL), \thfd)\right)
  \eeqn

@@

The model for the pushforward in the previous proposition appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KormanThesis} that converges to the cohomology with respect to the totalized differential $D+\thfd$ $H^{\bullet}(\cA_{\mathring M}(\cL), D+\thfd)$. In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where $M = Tot (\R\oplus \C^{2}\to \C^{3})$. We recall the result. Fix holomorphic coordinates $z_{i}, i=1, 2, 3$ on $\C^{3}$ and holomorphic fiber coordinates $w_{a}, a= 1, 2$ on $\C^{2}$.

\begin{prop}
Up to completion, the cohomology $H^{\bu}(\Gamma(\cA_{\mathring M}^{\bu}(\cL)), \thfD)$ is a direct sum of the cohomology on flat space $H^{\bu}(\gamma(\cA)$
\end{prop}

@@

After complexification, the~six-dimensional superconformal algebra is isomorphic to $\lie{osp}(8|4)$.
The even part of this algebra is $\lie{so}(8) \times \lie{sp}(4)$.
This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S^{6d}_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
%It also contains the three-dimensional $\cN=8$ supersymmetry algebra whose odd part is eight copies of $S^{3d}$, the irreducible complex spin representation of $\lie{so}(3)$.

The holomorphic supercharge is a supertranslation
\[
Q \in \Pi S^{6d}_+ \otimes \C^4 \subset \lie{osp}(8|4)
\]
which is characterized (up to equivalence) by the properties that $Q^2 = 0$ and that its image
\[
{\rm Im}\left(Q|_{\Pi S_+ \otimes \C^4} \right) \subset \R^6 \otimes_\R \C \cong \C^6
\]
is three-dimensional (spanned by the anti-holomorphic translations). 
The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.

%Similarly, the minimal twisting supercharge in the three-dimensional $\cN=8$ supersymmetry algebra is an element $Q \in \Pi S^{3d} \otimes \C^8$ which is characterized (up to equivalence) by the property that $Q^2 = 0$ and that the image of $[Q,-]$ is two-dimensional. The cohomology of $\lie{osp}(8|4)$ with respect to this supercharge is also isomorphic to~$\lie{osp}(6|2)$.

In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\lie{osp}(6|2)$. This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in \ref{hilbert} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.

We will enumerate states via their weights a Cartan in the bosonic subalgebra of the twisted superconformal algebra.
We recall below how the bosonic piece of the algebra
\beqn
\label{eqn:gut}
\lie{sl}(4) \times \lie{sl}(2) \subset \lie{osp}(6|2) 
\eeqn
embeds as symmetries, or ghosts, of the eleven-dimensional theory in this twisted background.

\brian{enhance to E(3|6)}.
However, we first note that the hilbert space $\cH_{sugra}$ in fact enjoys an action of a much larger symmetry algebra.

### 2022-09-21 fivebranes/twisted.tex
merge error

There is also the notion of the sheaf of holomorphic vector fields $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$.
Locally, on $\R^m \times \C^n$ these are vector fields of the form $f^i \del / \del z_i$ where each $f^i \in \cO_F$.
Let $\theta_F$ be the bundle $T_M \otimes \C / F$ on $M$ and declare 
$\cA^k(\theta_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^k F^* \otimes \theta_F$.
Then we obtain a resolution
\beqn
\vartheta_F \xto{\simeq} \left(\cA^\bu(\theta_F) , \thfd \otimes \id\right) .
\eeqn
The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(\theta_F)$ the structure of a dg Lie algebra.

Similarly, there is a resolution for the holomorphic one-forms as $\Omega^1_F \xto{\simeq} \cA^{1,\bu}_F$ where in degree $q$ the space $\cA^{1,q}_F$ is the sheaf of $C^\infty$-sections of $\wedge^q F^* \otimes \theta_F^*$.
Similarly, we let $\cA^{p,q}_F$ be the $C^\infty$-sections $\wedge^q F^* \otimes \wedge^p \theta_F^*$.

We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
Let us focus on the fields $\beta,\gamma$ which on $S \times X$ combine to form the complex
\beqn\label{eqn:drdol}
\Omega^{\bu}(S) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(S) \otimes \Omega^{1,\bu}(X) .
\eeqn
As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
There is an analog of this operator $1 \otimes \del$ on a manifold $M$ equipped with a THF~$F$.
It is a differential operator 
\beqn
D \colon \cA^{p,\bu}_F \to \cA^{p+1,\bu}_F
\eeqn
which locally is just the holomorphic de Rham operator. 
This operator commutes with $\thfd$.
The generalized $\beta$ and $\gamma$ fields will be sections of the two-term complex of sheaves $\cA^\bu_F \xto{D} \cA^{1,\bu}_F$.

>>>>

These furnish the notion of the sheaf of holomorphic vector fields $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$. These are the sheaves of sections of $Q$ and $Q^{*}$ that are flat with respect to the Bott connection. Locally, on $\R^m \times \C^n$ these are of the form $f^i \del / \del z_i$ and $f^{i}dz_{i}$ where each $f^i \in \cO_F$.

Let $\cA^k(Q), \cA^{k}(Q^{*})$ be the sheaves of $C^\infty$-sections of the bundles $\wedge^k F^{*} \otimes Q$ and $\wedge^{k}F^{*}\otimes Q^{*}$ respectively. Then we have resolutions

\beqn
\vartheta_F \xto{\simeq} \cA^\bu(Q) \\
\Omega^1_F \xto{\simeq}  \cA^\bu(Q^*)
\eeqn
The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(Q)$ the structure of a dg Lie algebra.

We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology. focus on the fields $\beta,\gamma$ which on $S \times X$ combine to form the complex
\beqn\label{eqn:drdol}
\Omega^{\bu}(S) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(S) \otimes \Omega^{1,\bu}(X) .
\eeqn
As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
There is an analog of this operator $1 \otimes \del$ on a manifold $M$ equipped with a THF~$F$.
It is a differential operator 
\beqn
D \colon \cA^{p,\bu}_F \to \cA^{p+1,\bu}_F
\eeqn
which locally is just the holomorphic de Rham operator. 
This operator commutes with $\thfd$.
The generalized $\beta$ and $\gamma$ fields will be sections of the two-term complex of sheaves $\cA^\bu_F \xto{D} \cA^{1,\bu}_F$.
